Extracting sunbeams from cucumbers: Reproducibility as a necessity for the future of archaeological science

### 2025-01-13 paper.qmd
reinsert some inline R code

n_articles <- nrow(items_df)
year_max <- max(items_df$year)
year_min <- min(items_df$year)
```

While Fanelli and Glänzel (2013) analysed papers published in a single year (2012), I found only 303 papers for that same year, and 70.2691554% of papers in the sample published after that date. To make efficient use of the available data and ensure robust representation from different areas of archaeology, including those with lower frequencies of journal article publication, I analysed 9697 papers published during 1975-2025. This sample was collected from Clarivate’s Web of Science database by first selecting the Web of Science category ‘Archaeology’ and the Document type ‘article’ (n = 28,871). To focus on journals of broad relevance to most archaeologists, and that are representative of substantial communities of practice, I then filtered the results to keep only articles published in the top-ranking 25 journals according to their h-indices as reported by Clarivate’s Journal Citation Indicator. Finally I excluded journals with less than 100 articles in the database.

>>>>

n_articles <- nrow(items_df)
year_max <- max(items_df$year)
year_min <- min(items_df$year)

items_df_2012 <- 
  items_df %>% 
  filter(year == 2012)

# how many archaeology articles in 2012
n_items_df_2012 <- nrow(items_df_2012)

# how many after 2012?
n_items_df_after_2012 <- 
  items_df %>% 
  filter(year %in% 2013:year_max) %>% 
  nrow()

# what proportion of archaeology articles published after 2012
prop_pub_after2012 <-  n_items_df_after_2012  / n_articles

While Fanelli and Glänzel (2013) analysed papers published in a single year (2012), I found only `r n_items_df_2012` papers for that same year, and `r round(prop_pub_after2012*100, 0)`% of papers in the sample published after that date. To make efficient use of the available data and ensure robust representation from different areas of archaeology, including those with lower frequencies of journal article publication, I analysed 9697 papers published during 1975-2025. This sample was collected from Clarivate’s Web of Science database by first selecting the Web of Science category ‘Archaeology’ and the Document type ‘article’ (n = 28,871). To focus on journals of broad relevance to most archaeologists, and that are representative of substantial communities of practice, I then filtered the results to keep only articles published in the top-ranking 25 journals according to their h-indices as reported by Clarivate’s Journal Citation Indicator. Finally I excluded journals with less than 100 articles in the database.
